Velocity Inversion by Surface Source Extension

### 2024-02-15 repro/papers/ms/paper.tex
cleaned up

To describe the problem setting more precisely, we introduce
notation that will be used throughout the discussion. Coordinates in
$\bR^3$ are $\bx=(x,y,z)$, $z$ representing depth. We assume that the
source and receiver wells are 
perfectly straight and vertical line segments in $\bR^3$(certainly an
idealization!), lying in the plane $y=0$: the
source ``well'' $W_s$and receiver ``well'' $W_r$ are defined by the
limit depths $z_s^{\rm min}$,$z_s^{\rm max}$,$z_r^{\rm min}$,$z_r^{\rm
  max}$: 
\begin{eqnarray}
\label{eqn:wells} 
W_s & = & \{\bx_s = (x_s,0,z_s): z_s^{\rm min} \le z_s \le z_s^{\rm 
          max}\} \nonumber \\
W_r & = & \{\bx_r = (x_r,0,z_r): z_r^{\rm min} \le z_r \le z_r^{\rm 
          max}\} 
\end{eqnarray}
As we will frequently need to refer to the depth ranges in the wells,
introduce
\begin{eqnarray}
\label{eqn:depths} 
Z_s & = & Z_s\} \nonumber \\
Z_r & = & Z_r\} 
\end{eqnarray}
We idealize energy sources as isotropic point radiators. A radiator at
$\bx=\bx_s$ appears as the right-hand side in the acoustic wave
equation, of the form $\delta(\bx-\bx_s)f(t)$. 
The function $f(t)$ is causal (vanishes on a negative half-axis, that
is,  for $t<<0$), and has units of
mass/time/time. The idealized model posits that every
source is has the same mechanism, modeled by the
isotropic point radiator with the same time dependence $f$, differing only in
depth $z=z_s$ in the source well.

Slowness (reciprocal velocity) turns out to be a more convenient
choice than velocity to represent the spatially varying acoustic
properties of the interwell material. We denote the slowness by $m$.
For physical reasons, $m$ should be positive and bounded uniformly above and 
below, say by $0 < m_{\rm min} < m_{\rm max}$. We assume that the
material is {\em acoustically transparent}, that is, generates no
reflected waves of significant energy in the seismic band. The geometric
optics approximation, to be summarized below, shows that a convenient
mathematical proxy for transparency is the assumption that $m$is
smooth, with derivatives up to
order 2 bounded by another constant $\mu > 0$. These conditions are
summarized in the definition of the feasible set of slowness models $M$:
\begin{equation}
\label{eqn:vfeas}
M=\{m \in C^{\infty}(\bR^3): m_{\rm min} < m(\bx) < m_{\rm max},
|D^{\alpha}m(\bx)| \le \mu,
\bx \in \bR^3, |\alpha| \le 2\}
\end{equation}

@@

\section{A Synthetic Example: FWI}
A simple 2D synthetic example illustrates the impact of Theorem
\ref{thm:FWIconv}. We will also use this example throughout the paper
to illustrate alternative solution methods for the crosswell inverse
problem.

The target slowness $m_*$ is the reciprocal of a piecewise
linear velocity (Figure
\ref{fig:velbig}). This corresponding velocity has a constant $2$ km/s layer near $x=0$ and
increases linearly for $x\ge 0.5$ km. Boundary conditions are Dirichlet
for pressure on all parts of the boundary, although the wavefields
occuring in the experiments described here interact only with the $x=0$
surface so that the effective geometry is that of a half-space. Data
for a single source at depth $x_s=$ 10 m, $z_s=$ 5100 m (coordinates as
depicted in Figure \ref{fig:velbig}. A line of receivers is positioned
at depth $x_r=$ 3000 m, with 4000 m $\le z_r \le$ 7000 m, spaced
$\Delta z_r$=30 m apart.

The source pulse ($f$ in equation (\ref{eqn:pressure})) is a [2.5, 5, 25, 30]
Hz trapezoidal bandpass filter produces the synthetic data
depicted in Figure \ref{fig:shot6kmbig}. Note that the finite
difference scheme used to produce this data approximates 2D wave
propagation rather than the 3D propagation mentioned in the discussion
so far, so that the data waveform is asymmetric, unlike the
source. Also the presence of the pressure-free surface near the source
contributes effectively another derivative. Nonetheless the data
resemble the prediction of the constant velocity calculation (equation
(\ref{eqn:cv})).

For a very smooth $m$ such as that depicted in Figure
\ref{fig:velbig}, the curve $z_r \mapsto \tau[m](z_s,z_r)$ resembles a hyperbola, as one sees from Figure
\ref{fig:shot6kmbig}. The onset time of the signal in this figure
depends on the slowness used in the simulation. For
$m_0 \equiv 0.5$ s/km, the predicted data $S[m_0]f$ are depicted in
Figure \ref{fig:shot6kmhom}. The general appearance is similar to   Figure
\ref{fig:shot6kmbig}, but the onset time of the wave is later, due to
the slower wave velocity.

Now consider the inverse problem (\ref{eqn:ls}) with $d=S[m_*]f$. Since
$m_*=m_0$ near the source point, it is not unreasonable to take $m_0$
as an initial guess for the wave velocity. Conventional FWI uses
iterative optimization algorithm to minimize $J_{\rm LS}$. Descent
algorithms related to Newton's method have been favored for FWI, due
to the computational cost of function evaluation
\cite[]{VirieuxOperto:09}. Of course, any such algorithm finds a
stationary point of the objective, assuming convergence, and not
necessarily a global minimizer.

A plot (Figure \ref{fig:fwicurve}) 
of $J_{\rm LS}$ along the line
segment from $m_0$ to $m_*$ immediately shows the difficulty faced by
a local optimization approach: as one
would predict from Theorem \ref{thm:FWIconv} and its proof, the predicted data change
little in size along this segment and have support nearly disjoint
from that of the target data $d$, hence are orthogonal to it, until the trial slowness becomes
quite close to the target $m_*$, so that the local behaviour of $J_{\rm LS}$ in a small
neighborhood of $m_0$ gives little or
no hint about a constructive update direction. One would not expect a
local optimization algorithm to be effective under such circumstances.

Most descent methods require computed gradient, as input to the
computation of a descent step. Assuming that $f \in H^1_0(\bR)$, the gradient of $J_{\rm LS}$ is 
\be\label{eqn:gradls}
\nabla J_{\rm LS}[m] = D(S[m]f)^T(w^2(S[m]f-d)).
\ee
In the expression \ref{eqn:gradls}, note that $m \rightarrow S[m]f$ is
a map from $M$ to $L^2(\Omega)$, the derivative of which is given in
equation  \ref{eqn:preq}. The symbol $D(S[m]f)^T$ denotes the
transpose of this derivative with respect to a Hilbert space norm
chosen for $M$, about which we have said nothing up to this point. We
will mention some sensible possibilities in the Discussion section;
for now, we simply identify $M$ with $L^2(\bR^2)$ for the purpose of
computing the transpose, hence the gradient of $J_{\rm LS}$. Thus the
gradient as computed here is the image of the formal or $L^2$ adjoint
of $D(S[m]f)$, applied
to the time-cutoff residual $w^2(S[m]f-d)$. 
%There is no reason to suppose that this
%image would be smooth, given the weak constraints on $f$ and $d$, so
%in general it will not define an acceptable update direction for
%velocity. One way out of this predicament is to extend the domain of
%$S$ to a subset of a larger Hilbert space containing
%$C^{\infty}(\bR^2)$, defined by control of finitely many derivatives,
%such as a Sobolev space, and define the adjoint with respect to this
%inner product structure, obtained by concatenating a smoothing
%operator with the formal adjoint. The reader can consult for instance
%\cite{KerSy:94} for more on this idea. For the purposes of this
%discussion we will display the formal gradient (\ref{eqn:gradls})..

Figure \ref{fig:fwigrad6kmbighom} shows the result of the computation
(\ref{eqn:gradls}) for the example given previously, $m=m_0$, $d=S[m_*]f$. The adjoint $D(S[m]f)^T$ is
computed by the adjoint state method
\cite[]{Chavent:74,GauTarVir:86,Plessix:06}. Geometric optics explains
the apparent interrogation of only the triangle spanning the source
and the receiver segment - perturbations of velocity outside of it do
not affect the geometric optics travel times (rays are straight lines,
in constant velocity) connecting source and receivers. However there
is very little indication of a productive update: the edge effects one
sees in this figure (``rabbit ears'') average to very nearly zero when
weighted by the difference between $m_0$ and $m_*$ - that is, the
gradient is essentially orthogonal to the best search direction.

If we use the gradient as a search direction, as one would for the
steepest descent algorithm, for instance, then one obtains the values
of $J_{\rm LS}$ displayed in Figure \ref{fig:fwigrad} - clearly not a
productive search direction.

@@

\inputdir{project}
%\plot{csqlens10}{width=\textwidth}{Lens: diameter = 0.5 km, thickness = 1.0 km, background velocity = 2 km/s, velocity at center = 1.4142  km/s.}
%\plot{shot6kmlens10conv}{width=\textwidth}{Shot gather - source at x=5100 m, z=10 m. Receivers between 4 km and 6km at depth = 3.0 km.}
%\plot{awicurve}{width=\textwidth}{RMS amplitudes of inversions for
%trace-dependent source (matched source), scaled by t (second moment
%objective). Convex combinations of homogeneous (2 km/s) and lens models.}
\plot{velbig_dec_exp}{width=\textwidth}{Example: $v$ = 2 km/s for $z \le
  0.5 km$, $=2.0 + (z-0.5)*0.5$ km/s for $z>0.5$ km. Source location
  $x=5100$, $z=10$ m and receiver locations $x=3000 - 6000$ m,
$z=3000$ m indicated.}
\plot{shot6kmhom}{width=\textwidth}{Shot gather for geometry indicated
  in Figure \ref{fig:velbig_dec_exp}, generated with homogeneous velocity:
  $v_0=2$ km/s}
\plot{shot6kmbig}{width=\textwidth}{Shot gather for geometry and
  $v$ as in Figure \ref{fig:velbig_dec_exp}.}
\plot{shot6kmbig_decon}{width=\textwidth}{Inverse image of data in 
  Figure (\ref{shot6kmbig}) under extended modeling operator at $v_0$
  = 2 km/s}
\plot{shot6kmbig_bigdecon}{width=\textwidth}{Inverse image of data in 
  Figure \ref{shot6kmbig} under extended modeling operator at target
  $v$ (Figure \ref{fig:velbig_dec_exp}).}
\plot{fwigrad6kmbighom}{width=\textwidth}{FWI gradient for shot gather
defined in Figure \ref{fig:velbig_dec_exp}, at $v=v_0$ = 2 km/s. Scaled by
10$^6$ for plotting. Note very
small values, and sign is positive, indicating that FWI objective {\em
increases} in the direction of the target velocity.}
\plot{fwiscan}{width=\textwidth}{Plot of values of the FWI objective
  along the line segment between $v_0$ and $v$, for the shot gather
  described in Figure \ref{fig:velbig_dec_exp}. For abscissa $h$, value
  plotted is FWI objective at $h v_0 + (1-h) v$. Note that objective
  does in fact initially increase from its value at $v_0$, consistent
  with the positive average value of the gradient as shown in Figure \ref{fig:fwigrad6kmbighom}. }
\plot{ivagrad6kmbighom}{width=\textwidth}{Source-receiver Extended FWI
  gradient, same geometry, data, and velocity model as in Figure
  \ref{fig:fwigrad6kmbighom}. Note that overall sign is negative, indicating
  correct conclusion that $v_0$ is slow.}
\plot{fwistack}{width=\textwidth}{FWI gradient at $v=v_0$ for line of shots 
  extending from 2100 m to 8000 m. Scaled by
10$^6$ for plotting. Receiver locations are windowed so 
  that the range of offsets is the same for all shots. In effect, the 
  gradient is a stack of translates of the gradient in Figure
  \ref{fig:fwigrad6kmbighom}.}
\plot{ivastack}{width=\textwidth}{Source-receiver Extended FWI gradient at $v=v_0$ for line of shots 
  extending from 2100 m to 8000 m. Receiver locations are windowed so 
  that the range of offsets is the same for all shots. In effect, the 
  gradient is a stack of translates of the gradient in Figure
  \ref{fig:ivagrad6kmbighom}.}

>>>>

To describe the problem setting more precisely, we introduce
notation that will be used throughout the discussion. Coordinates in
$\bR^3$ are $\bx=(x,y,z)$, $z$ representing depth. We assume that the
source and receiver wells are 
perfectly straight and vertical line segments in $\bR^3$(certainly an
idealization!), lying in the plane $y=0$: the
source ``well'' $W_s$and receiver ``well'' $W_r$ are defined by the
limit depths $z_s^{\rm min}$,$z_s^{\rm max}$,$z_r^{\rm min}$,$z_r^{\rm
  max}$: 
\begin{eqnarray}
\label{eqn:wells} 
W_s & = & \{\bx_s = (x_s,0,z_s): z_s^{\rm min} \le z_s \le z_s^{\rm 
          max}\} \nonumber \\
W_r & = & \{\bx_r = (x_r,0,z_r): z_r^{\rm min} \le z_r \le z_r^{\rm 
          max}\} 
\end{eqnarray}
As we will frequently need to refer to the depth ranges in the wells,
introduce
\begin{eqnarray}
\label{eqn:depths} 
Z_s & = & [z_s^{\rm min}, z_s^{\rm max}] \nonumber \\
Z_r & = & [z_r^{\rm min},z_r^{\rm max}] 
\end{eqnarray}
We idealize energy sources as isotropic point radiators. A radiator at
$\bx=\bx_s$ appears as the right-hand side in the acoustic wave
equation, of the form $\delta(\bx-\bx_s)f(t)$. 
The function $f(t)$ is causal (vanishes on a negative half-axis, that
is,  for $t<<0$), and has units of
mass/time/time. The idealized model posits that every
source is has the same mechanism, modeled by the
isotropic point radiator with the same time dependence $f$, differing only in
depth $z=z_s$ in the source well.

Slowness (reciprocal velocity) turns out to be a more convenient
choice than velocity to represent the spatially varying acoustic
properties of the interwell material. We denote the slowness by $m$.
For physical reasons, $m$ should be positive and bounded uniformly above and 
below, say by $0 < m_{\rm min} < m_{\rm max}$.

We assume that the
material is {\em acoustically transparent}, that is, generates no
reflected waves of significant energy in the seismic band. The geometric
optics approximation, to be summarized below, shows that a convenient
mathematical proxy for transparency is the assumption that $m$ is
smooth, with derivatives up to
order 2 bounded by another constant $\mu > 0$. These conditions are
summarized in the definition of the feasible set of slowness models $M$:
\begin{equation}
\label{eqn:vfeas}
M=\{m \in C^{\infty}(\bR^3): m_{\rm min} < m(\bx) < m_{\rm max},
|D^{\alpha}m(\bx)| \le \mu,
\bx \in \bR^3, |\alpha| \le 2\}
\end{equation}

@@

@@

\inputdir{project}
%\plot{csqlens10}{width=\textwidth}{Lens: diameter = 0.5 km, thickness = 1.0 km, background velocity = 2 km/s, velocity at center = 1.4142  km/s.}
%\plot{shot6kmlens10conv}{width=\textwidth}{Shot gather - source at x=5100 m, z=10 m. Receivers between 4 km and 6km at depth = 3.0 km.}
%\plot{awicurve}{width=\textwidth}{RMS amplitudes of inversions for
%trace-dependent source (matched source), scaled by t (second moment
%objective). Convex combinations of homogeneous (2 km/s) and lens models.}
%\plot{./velbig_dec}{width=\textwidth}{Example: $v$ = 2 km/s for $z \le
%  0.5 km$, $=2.0 + (z-0.5)*0.5$ km/s for $z>0.5$ km. Source location
%  $x=5100$, $z=10$ m and receiver locations $x=3000 - 6000$ m,
%$z=3000$ m indicated.}
%\plot{shot6kmhom}{width=\textwidth}{Shot gather for geometry indicated
%  in Figure \ref{fig:velbig_dec_exp}, generated with homogeneous velocity:
%  $v_0=2$ km/s}
%\plot{shot6kmbig}{width=\textwidth}{Shot gather for geometry and
%  $v$ as in Figure \ref{fig:velbig_dec_exp}.}
%\plot{shot6kmbig_decon}{width=\textwidth}{Inverse image of data in 
%  Figure (\ref{shot6kmbig}) under extended modeling operator at $v_0$
%  = 2 km/s}
%\plot{shot6kmbig_bigdecon}{width=\textwidth}{Inverse image of data in 
%  Figure \ref{shot6kmbig} under extended modeling operator at target
%  $v$ (Figure \ref{fig:velbig_dec_exp}).}
%\plot{fwigrad6kmbighom}{width=\textwidth}{FWI gradient for shot gather
%defined in Figure \ref{fig:velbig_dec_exp}, at $v=v_0$ = 2 km/s. Scaled by
%10$^6$ for plotting. Note very
%small values, and sign is positive, indicating that FWI objective {\em
%increases} in the direction of the target velocity.}
%\plot{fwiscan}{width=\textwidth}{Plot of values of the FWI objective
%  along the line segment between $v_0$ and $v$, for the shot gather
%  described in Figure \ref{fig:velbig_dec_exp}. For abscissa $h$, value
%  plotted is FWI objective at $h v_0 + (1-h) v$. Note that objective
%  does in fact initially increase from its value at $v_0$, consistent
%  with the positive average value of the gradient as shown in Figure \ref{fig:fwigrad6km%bighom}. }
%\plot{ivagrad6kmbighom}{width=\textwidth}{Source-receiver Extended FWI
%  gradient, same geometry, data, and velocity model as in Figure
%  \ref{fig:fwigrad6kmbighom}. Note that overall sign is negative, indicating
% correct conclusion that $v_0$ is slow.}
%\plot{fwistack}{width=\textwidth}{FWI gradient at $v=v_0$ for line of shots 
%  extending from 2100 m to 8000 m. Scaled by
%10$^6$ for plotting. Receiver locations are windowed so 
%  that the range of offsets is the same for all shots. In effect, the 
%  gradient is a stack of translates of the gradient in Figure
%  \ref{fig:fwigrad6kmbighom}.}
%\plot{ivastack}{width=\textwidth}{Source-receiver Extended FWI gradient at $v=v_0$ for line of shots 
%  extending from 2100 m to 8000 m. Receiver locations are windowed so 
%  that the range of offsets is the same for all shots. In effect, the 
%  gradient is a stack of translates of the gradient in Figure
%  \ref{fig:ivagrad6kmbighom}.}

### 2024-02-15 repro/papers/sseprecond/paper.tex
cleaned up

@@

@@

@@

>>>>

%#############

Another figure \ref{fig:ddifffwdaltplh0}
More figures: \ref{fig:compnrestrunc0lh0}, \ref{fig:compnrestrunc1lh0}.

@@

\plot{compnrestrunc0lh0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in homogenous model. Penalty weight 
  $\alpha=0$.}

\plot{compnrestrunc0ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight 
  $\alpha=0$.}

@@

\plot{compnrestrunc1lh0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

\plot{compnrestrunc1ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight
  $\alpha=10^{-3}$.}
\newpage

\plot{ddifffwdaltplh0}{width=\textwidth}{Diff}

@@

\section{More plots}

A plot of the model with rays overlain, \ref{fig:olensrays0}.

\plot{olensrays0}{width=\textwidth}{Lens model with rays.}

### 2024-02-15 repro/papers/sseprecond/plots.tex
cleaned up

The upshot is the cycle represented in the figures \ref{fig:srcvzhh0},  \ref{fig:resrcvzhh0}, \ref{fig:srcvzlh0},  \ref{fig:resrcvzlh0}. Figure \ref{fig:srcvzhh0} is the normal component of velocity at $z_s=3$ km of backpropagation, from the field with pressure trace displayed in Figure \ref{fig:ptpwindh0} at $z_r=1$ km, propagation and backpropagation in homogeneous material model with $\kappa = $ 4 Gpa, $\rho = $ 1 g/m$^{-6}$.The pressure trace at $z=z_s$ was also recorded, and used to recompute the normal velocity trace \ref{fig:resrcvzhh0}. The difference is displayed as figure \ref{fig:dresrcvzhh0}.

Similarly, Figure \ref{fig:srcvzlh0} is the normal component of velocity at $z_s=3$ km of backpropagation, from the field with pressure trace displayed in Figure \ref{ptpwindl0} at $z_r=1$ km, propagation in the model with the model with bulk modulus displayed in Figure \ref{fig:bml0} and density $\rho = $ 1 g/m$^{-6}$, and backpropagation in the homogeneous model with bulk modulus = 4 GPa. The pressure trace at $z=z_s$ was also recorded, and used to recompute the normal velocity trace \ref{fig:resrcvzlh0}. The difference is displayed as figure \ref{fig:dresrcvzlh0}.

@@

>>>>

The upshot is the cycle represented in the figures \ref{fig:srcvzhh0},  \ref{fig:resrcvzhh0}, \ref{fig:srcvzlh0},  \ref{fig:resrcvzlh0}. Figure \ref{fig:srcvzhh0} is the normal component of velocity at $z_s=3$ km of backpropagation, from the field with pressure trace displayed in Figure \ref{fig:ptpwindhh0} at $z_r=1$ km, propagation and backpropagation in homogeneous material model with $\kappa = $ 4 Gpa, $\rho = $ 1 g/m$^{-6}$.The pressure trace at $z=z_s$ was also recorded, and used to recompute the normal velocity trace \ref{fig:resrcvzhh0}. The difference is displayed as figure \ref{fig:dresrcvzhh0}.

Similarly, Figure \ref{fig:srcvzlh0} is the normal component of velocity at $z_s=3$ km of backpropagation, from the field with pressure trace displayed in Figure \ref{ptpwindll0} at $z_r=1$ km, propagation in the model with the model with bulk modulus displayed in Figure \ref{fig:bml0} and density $\rho = $ 1 g/m$^{-6}$, and backpropagation in the homogeneous model with bulk modulus = 4 GPa. The pressure trace at $z=z_s$ was also recorded, and used to recompute the normal velocity trace \ref{fig:resrcvzlh0}. The difference is displayed as figure \ref{fig:dresrcvzlh0}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%

\plot{recphh0}{width=15cm}{Pressure data, homogeneous velocity model}

\plot{rerecphh0}{width=15cm}{Resimulated pressure traces, Input data simulated in homogeneous velocity model (Figure \ref{fig:recphh0}). Resimulation source computed from p traces at receivers only, backpropagated in homogeneous velocity model.}

\plot{reptr21hh0}{width=15cm}{Resimulated pressure trace 21, from data simulated in homogeneous velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr51hh0}{width=15cm}{Resimulated pressure trace 51, from data simulated in homogeneous velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr81hh0}{width=15cm}{Resimulated pressure trace 81, from data simulated in homogeneous velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{recplh0}{width=15cm}{Pressure data, lens velocity model}

\plot{rerecplh0}{width=15cm}{Resimulated pressure traces, Input data simulated in lens velocity model (Figure \ref{fig:recplh0}). Resimulation source computed from p traces at receivers only, backpropagated in homogeneous velocity model.}

\plot{reptr21lh0}{width=15cm}{Resimulated pressure trace 21, from data simulated in lens velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr51lh0}{width=15cm}{Resimulated pressure trace 51, from data simulated in lens velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr81lh0}{width=15cm}{Resimulated pressure trace 81, from data simulated in lens velocity model, backpropagated in homogeneous velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{rerecpll0}{width=15cm}{Resimulated pressure traces, Input data simulated in lens velocity model (Figure \ref{fig:recplh0}). Resimulation source computed from p traces at receivers only, backpropagated in lens velocity model.}

\plot{reptr21ll0}{width=15cm}{Resimulated pressure trace 21, from data simulated in lens velocity model, backpropagated in lens velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr51ll0}{width=15cm}{Resimulated pressure trace 51, from data simulated in lens velocity model, backpropagated in lens velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

\plot{reptr81ll0}{width=15cm}{Resimulated pressure trace 81, from data simulated in lens velocity model, backpropagated in lens velocity model. Red: target data. Blue: resimulated data, with resimulationsource computed from p traces at receivers only.}

### 2024-02-15 repro/papers/ssevelan/paper.tex
cleaned up

\inputdir{../trans/project}

@@

Then 
$\oS_1[\kappa]$ has a microlocal approximate inverse $(\oS[\kappa]^1)^{\dagger}$, defined by 
\begin{equation}
\label{eqn:appinv}
\oS_1^{\dagger} = W_s^{-1}\oS_1^TW_r
\end{equation}
in which $W_s, W_r$ are properly supported $\Psi$DOs on $\Gamma_s \times \bR,\Gamma_r \times \bR$ respectively [from here on, suppress the arguments whenever these are obvious: $\oS_1 = \oS_1[\kappa]$ and so on]. The sense in which $\oS_1^{\dagger}$ is an inverse is that
\begin{eqnarray}
\label{eqn:proj}
\oS_1^{\dagger}\oS &=& \Pi^1_s\\
\oS \oS_1^{\dagger} &=& \Pi^1_r
\end{eqnarray}
in which $\Pi^1_{s,r} \in OPS^0(\Gamma_{s,r}\times \bR)$ have principal symbols $\sim 1$ in the conic sets $\gamma_{s,r} \subset T^*(\Gamma_{s,r}\times \bR)$.
%, and $\ge 1/2$ in the larger conic sets $\tilde{\gamma}^1_{s,r} \supset \gamma^1_{s,r}$.

@@

\begin{theorem}
\label{d2j}
Suppose that $d=S\tilde{\Pi}f_{\lambda}$ is $r$-approximately point and $\{f_{\lambda}\}$ is a high-frequency wavelet family. Then
\[
D^2\Jared = \|[Q,A_r]\ofa\|^2 + O(\lambda^2)
\]
\end{theorem}

@@

>>>>

\inputdir{project}

@@

Then 
$\oS_1[\kappa]$ has a microlocal approximate inverse $(\oS[\kappa]^1)^{\dagger}$, defined by 
\begin{equation}
\label{eqn:appinv}
\oS_1^{\dagger} = W_s^{-1}\oS_1^TW_r
\end{equation}
in which $W_s, W_r$ are properly supported $\Psi$DOs on $\Gamma_s \times \bR,\Gamma_r \times \bR$ respectively [from here on, suppress the arguments whenever these are obvious: $\oS_1 = \oS_1[\kappa]$ and so on]. The sense in which $\oS_1^{\dagger}$ is an inverse is that
\begin{eqnarray}
\label{eqn:proj}
\oS_1^{\dagger}\oS_1 &=& \Pi^1_s\\
\oS_1 \oS_1^{\dagger} &=& \Pi^1_r
\end{eqnarray}
in which $\Pi^1_{s,r} \in OPS^0(\Gamma_{s,r}\times \bR)$ have principal symbols $\sim 1$ in the conic sets $\gamma_{s,r} \subset T^*(\Gamma_{s,r}\times \bR)$.
%, and $\ge 1/2$ in the larger conic sets $\tilde{\gamma}^1_{s,r} \supset \gamma^1_{s,r}$.

@@

\begin{theorem}
\label{d2j}
Suppose that $d=S\tilde{\Pi}f_{\lambda}$ is $r$-approximately point and $\{f_{\lambda}\}$ is a high-frequency wavelet family. Then
\[
D^2\Jared = \alpha^2\|[Q,A_r]\ofa\|^2 + O(\lambda^2)
\]
\end{theorem}

@@

% \plot{ptsrc00}{width=\textwidth}{Bandpass filter pulse}

\plot{bml0}{width=\textwidth}{Lens model}
\plot{plbulksm0}{width=\textwidth}{Layered model}
\plot{oplrays0}{width=\textwidth}{Diving ray model}
\plot{ooplrays0}{width=\textwidth}{Diving ray model}
\plot{ndwdata0}{width=\textwidth}{Muted point source data}
\plot{ndwdatavz0}{width=\textwidth}{Muted point source data}
\plot{ndwdataresrcplbulksm0}{width=\textwidth}{Muted point source data}
\plot{ndwdataresimplbulksm0}{width=\textwidth}{Muted point source
  data}
\plot{ndwdatarediffplbulksm0}{width=\textwidth}{Muted point source data}
\plot{ndwraw0}{width=\textwidth}{Point source data}
\plot{ndwmute0}{width=\textwidth}{Mute function}

\plot{ooxtraysend}{width=\textwidth}{Ray crossing times $z=0$}
